HPC--101\\Onboarding

### 2016-04-07 hpc_101/cheatsheet/paper.tex
update of author list to include director

\begin{document}
\setlength{\droptitle}{-10em}
\title{HPC--101 -- Cheatsheet \vspace{-2ex}}
\date{\today}
\author{Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.\\~\\University of {\hawaii}\\Information Technology Services -- {\ci}}
\maketitle
\section{Directory Navigation}
\begin{itemize}
\item[] \texttt{cd {\pth{Directory}}}\desc{Change to directory specified}
\item[] \texttt{ls {\pth{Path}}}\desc{List the contents of the specified path}
\item[] \texttt{ls -l {\pth{Path}}}\desc{This flag list the paths content in long form}
\item[] \texttt{ls -lh {\pth{Path}}}\desc{Make the filesize humanreable}
\item[] \texttt{ls -a {\pth{Path}}}\desc{Show hidden directories and files}
%\item[] pwd \desc{Print working directory}
\end{itemize}

>>>>

\begin{document}
\setlength{\droptitle}{-10em}
\title{HPC--101 -- Cheatsheet \vspace{-2ex}}
\date{\today}
\author{Gwen Jacobs Ph.D,\\Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.\\~\\University of {\hawaii}\\Information Technology Services -- {\ci}}
\maketitle
\section{Directory Navigation}
\begin{itemize}
\item[] \texttt{cd {\pth{Directory}}}\desc{Change to directory specified}
\item[] \texttt{ls {\pth{Path}}}\desc{List the contents of the specified path}
\item[] \texttt{ls -l {\pth{Path}}}\desc{This flag list the paths content in long form}
\item[] \texttt{ls -lh {\pth{Path}}}\desc{Make the filesize humanreable}
\item[] \texttt{ls -a {\pth{Path}}}\desc{Show hidden directories and files}
%\item[] pwd \desc{Print working directory}
\end{itemize}

### 2016-04-07 hpc_101/paper.tex
update of author list to include director

\author{Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.\\~\\Director\\Gwen Jacobs Ph.D}
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

@@

\subsubsection{Hardware}
\begin{frame}
	\frametitle{{\craycs} -- Compute Nodes}
	\begin{itemize}
        \item All nodes are diskless with some RAM used for the Operating System
	\item 178 Standard nodes
	  \begin{itemize}
            {\footnotesize
	    \item Two 10 core {\intel} Ivy-Bridge processors (\emph{20 cores total})
	    \item 128GB of physical RAM with $\approx110$GB of useable RAM
            }
	  \end{itemize}

	\item 6 Large memory nodes
	  \begin{itemize}
            {\footnotesize
	    \item Four 10 core {\intel}  Ivy-Bridge processors (\emph{40 cores total})
	    \item 1TB of physical RAM with $\approx1008$GB of useable RAM
            }
	  \end{itemize}			
        \item 1 GPU node
          \begin{itemize}
            {\footnotesize
	    \item Two 10 core {\intel} Haswell processors (\emph{20 cores total})
	    \item 128GB of physical RAM with $\approx110$GB of useable RAM
            \item 2 Nvidia Tesla K40 GPUs
            }
	  \end{itemize}
        \item 91 Owner nodes
          \begin{itemize}
            {\footnotesize
            \item 33 nodes have two 10 core {\intel} Haswell processors with 256 GB of RAM
            \item 58 nodes have two 12 core {\intel} Haswell processors with 128 GB of RAM
            }
          \end{itemize}
	\item CentOS Linux
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ ValueStorage}
	\begin{itemize}
		\item $500$TB of scale out storage
		\item Currently only available for purchase by cluster users and only accessible via the login nodes
		\item ValueStorage will eventually be available for purchase by everyone
		\item ValueStorage owners will potentially be able to mount as a network drive (CIFS) on laptop, workstations, servers
		\item Purchased in 0.5TB increments
	\end{itemize}
	\btVFill

>>>>

\author{Gwen Jacobs Ph.D,\\Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.}
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

@@

\subsubsection{Hardware}
\begin{frame}
	\frametitle{{\craycs} -- Compute Nodes}
	\begin{itemize}
        \item All nodes are diskless with some RAM used for the Operating System
	\item 178 Standard nodes
	  \begin{itemize}
            {\footnotesize
	    \item Two 10 core {\intel} Ivy-Bridge processors (\emph{20 cores total})
	    \item 128GB of physical RAM with $\approx118$GB of useable RAM
            }
	  \end{itemize}

	\item 6 Large memory nodes
	  \begin{itemize}
            {\footnotesize
	    \item Four 10 core {\intel}  Ivy-Bridge processors (\emph{40 cores total})
	    \item 1TB of physical RAM with $\approx1000$GB of useable RAM
            }
	  \end{itemize}			
        \item 1 GPU node
          \begin{itemize}
            {\footnotesize
	    \item Two 10 core {\intel} Haswell processors (\emph{20 cores total})
	    \item 128GB of physical RAM with $\approx118$GB of useable RAM
            \item 2 Nvidia Tesla K40 GPUs
            }
	  \end{itemize}
        \item 91 Owner nodes
          \begin{itemize}
            {\footnotesize
            \item 33 nodes have two 10 core {\intel} Haswell processors with 256 GB of RAM
            \item 58 nodes have two 12 core {\intel} Haswell processors with 128 GB of RAM
            }
          \end{itemize}
	\item CentOS Linux
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ ValueStorage}
	\begin{itemize}
		\item $500$TB of scale out storage
		\item Is only available for purchase by cluster users~\\and only accessible via the login nodes
		\item Purchased in 0.5TB increments
	\end{itemize}
	\btVFill
